Manuscript

### 2016-03-14 inst/simulation/manuscript.Rmd
...

plotCIProportions <- function(credibilityIntervals) {
  credibilityIntervals$Model <- prettyModelName(credibilityIntervals$modelName)
  credibilityIntervals$CrI <- credibilityIntervals$Interval
  p <- ggplot(credibilityIntervals, aes(scenario, Proportion, shape=Model, colour=CrI)) +
    geom_hline(aes(yintercept=.5), color="darkgrey") +
    geom_hline(aes(yintercept=.95), color="darkgrey") +
    geom_point(aes(shape=Model, group=Model), position=position_dodge(width=.7)) +
    scale_colour_manual("CrI", values=c("black", "grey"), guide=guide_legend(override.aes=list(size=3.5, shape=15))) +
    theme_ms() +
    theme(panel.border=element_rect(fill="transparent")) +
    xlab("Scenario") + ylab("Proportion") + ylim(0, 1) +
    theme(panel.grid.major=element_blank(), panel.grid.minor=element_blank(),
          panel.margin=unit(0, units="line"),
          legend.direction="vertical",
          legend.box="horizontal",
          legend.key.height=unit(0.7, "line"))
    #guides(scale_colour_manual=guide_colourbar())

>>>>

plotCIProportions <- function(credibilityIntervals) {
  credibilityIntervals$Model <- prettyModelName(credibilityIntervals$modelName)
  credibilityIntervals$CrI <- credibilityIntervals$Interval
  p <- ggplot(credibilityIntervals, aes(scenario, Proportion, shape=Model, colour=CrI)) +
    geom_hline(aes(yintercept=.5), color="darkgrey") +
    geom_hline(aes(yintercept=.95), color="darkgrey") +
    geom_point(aes(shape=Model, group=Model), position=position_dodge(width=.7)) +
    scale_colour_manual("CrI / CI", values=c("black", "grey"), guide=guide_legend(override.aes=list(size=3.5, shape=15))) +
    theme_ms() +
    theme(panel.border=element_rect(fill="transparent")) +
    xlab("Scenario") + ylab("Proportion") + ylim(0, 1) +
    theme(panel.grid.major=element_blank(), panel.grid.minor=element_blank(),
          panel.margin=unit(0, units="line"),
          legend.direction="vertical",
          legend.box="horizontal",
          legend.key.height=unit(0.7, "line"))
    #guides(scale_colour_manual=guide_colourbar())
